% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
\usepackage{enumitem}
\usepackage{tabto}
\usepackage{fontspec}
\usepackage{amssymb}
\usepackage{eurosym}
\usepackage[Symbols]{ucharclasses}
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10.7in} % increase text height to fit resume on 1 page
\setlist[itemize,1]{leftmargin=\dimexpr 26pt-.7in} % to change the tab size globally
\addtolength{\textwidth}{0.8in}
\addtolength{\hoffset}{-0.5in}

\usepackage{fontawesome5}
\newfontfamily{\mysymbolfont}{Symbola}
\newfontfamily{\mymainfont}{DejaVu Sans}
\setTransitionsForSymbols{\mysymbolfont}{}

\begin{document}  
\ifisanon
        \name{ANONYMOUS CV}
        \address{Some parts were removed. These are highlighted by \textit{(Anonymous)}}
\else
        \name{SAMUEL GIFFARD}

        \address{ \faMapMarker*~Pietersbergweg 53-B, 1105 BM, Amsterdam, NL ~~ \faPassport~France \\ \faAt~samuel@giffard.co ~~ \faMobile*~+32 (0) 4-84-14-10-33 ~~ \faMobile*~+33 (0) 7-69-69-12-02 \\ \\ \textbf{\faPython~Python Trainer, Engineer \& Evangelist} }
\fi

\begin{resume}
 
\section{\faGraduationCap~EDUCATION}
\begin{itemize} 
\item[] 2011 - 2012 \tabto{2cm} MSc Computer Science \hfill University of Edinburgh -- Scotland 
        \begin{itemize}
                \item[+] \textbf{MSc Computer Science with Distinction} in Computer Systems, Software Engr. and High Perf. Computing
        \end{itemize}
        
\item[] 2009 - 2011 \tabto{2cm} BSc (Hons) Computer Science \hfill Robert Gordon University -- Scotland 
        \begin{itemize}
                \item[+] \textbf{First-class Bachelor with Honours} in Computing for Internet and Multimedia
        \end{itemize}
        
\item[] 2008 - 2009 \tabto{2cm} Licence 3 Informatique Fondamentale \hfill Toulouse III (Universit\'e Paul Sabatier) -- France
        \begin{itemize}
                \item[+] Equivalent: third year of BSc, Fundamentals in Computer Science
        \end{itemize}

\item[] 2007 - 2008 \tabto{2cm} \textbf{DUT Informatique} \hfill IUT ``A'' -- Toulouse III -- France
        \begin{itemize}
                \item[+] Equivalent: HND Computing
                \item[+] Two-year University degree in Computer Science, in one intensive year (called ``Ann\'ee Sp\'eciale'')
        \end{itemize}

\item[] 2006 - 2007 \tabto{2cm} CPGE TSI \hfill Lyc\'ee Jean-Baptiste Dumas -- Al\`es -- France
        \begin{itemize}
                \item[+] Preparation for national competitive entrance exams to leading French ``Grandes \'Ecoles'', specializing in Mathematics and Physics
        \end{itemize}
        
\item[] 2006 \tabto{2cm} Baccalaur\'eat, in Electronics \hfill Lyc\'ee Antoine Bourdelle -- Montauban -- France
        \begin{itemize}
                \item[+] Equivalent: A-Levels
                \item[+] \textbf{Bac STI G\'enie \'Electronique mention Bien} (top 10\%, $\sim$ with Honours)
        \end{itemize}
\end{itemize}


\section{\faMedal~ACHIEVEMENTS}
\begin{itemize}
        \item[] April 18, 2018 \tabto{4cm} Python Challenge Europe 2018 \textbf{Winner Pro} (by Cisco, EDITx, ECAM)
        \item[] July 15, 2011 \tabto{4cm} Graduated as \textbf{Valedictorian} 2010-2011
        \item[] July 1, 2011 \tabto{4cm} Awarded the \textbf{Nexen Prize} for the highest academic achievement
\end{itemize}


\section{\faLayerGroup~SKILLS}
        \begin{itemize}
                \item[] \faLanguage~\textbf{Languages}
                \begin{itemize}
                 \item[+]  \textbf{French}: native, \textbf{English}: bilingual, \textbf{Spanish}: $\approx$B1, \textbf{Dutch}: $\approx$A2, \textbf{Japanese}: $\approx$A1
                \end{itemize}   
        \end{itemize}
        
        \begin{itemize}
        \item[] \faLaptopCode~\textbf{Computer}
                \begin{itemize}
                  \item[+] \textbf{Concepts}: Architecture, Multimedia, Security, Relational Databases, Distributed \& Advanced Databases, High-Performance Computing, Object-Oriented, Complexity, Hadoop, Continuous Integration / Deployment
                  \item[+] \textbf{Software}: Oracle, PyCharm, Eclipse, Xcode, PDB, GDB, Valgrind, Adobe (Dw, Ps, Sb, Fl), git, Jenkins
                  \item[+] \textbf{Languages}: \textbf{Python}, FastAPI, Django, \textbf{C/C++}, Linux BASH, MySQL, SQLite, \textbf{Oracle PL/SQL}, EdgeDB, Objective-C (iOS), JAVA, ARM, OpenGL (Glut), \LaTeX{}, JS, jQuery, PHP, HTML5/CSS3, XML (XPath, XQuery, DTD, XSD, XSLT), Bubble.io
                \end{itemize}
        \end{itemize}

        \begin{itemize}
        \item[] \faHandshake[regular]~\textbf{Leadership}
                \begin{itemize}
                   \item[+] Elected twice as President of ASSERP, the Student Association in Ponsan-Bellevue (Toulouse -- France). I~coordinated the management of over ten societies, each with their own president
                  \item[+] Head Judge for the international game \textit{Magic: The Gathering} in Nice -- France
                  \item[+] Lead several group projects to their completion and success
                \end{itemize}   
        \end{itemize}
        
        \begin{itemize}
        \item[] \faComments[regular]~\textbf{Communication}
            \begin{itemize}
							\item[+] In Amadeus, supervised interns for three months on Django and for six months on Node.js / Aria Template.
                \item[+] Judge for \textit{MTG}, communication within a team and communication with players. Most of the tournaments had over 120 players and last for over 14 hours
                \item[+] Worked as part of customer facing teams in Pizzerias, Restaurants, Tea house
                \item[+] Led training courses for students in school: Technology in Middle School, Montauban -- France
                \item[+] Led campus tours at RGU, Aberdeen -- Scotland
            \end{itemize} 
        \end{itemize}

\pagebreak

\section{\faBriefcase~WORK EXPERIENCES}
        \begin{itemize}
                    \item[] \textbf{Since Feb. 2022} \tabto{5cm} Software Engineer (Python) \hfill Amsterdam -- Netherlands
                    \begin{itemize}
                        \item[+] Python developer for \textbf{Picnic}'s Python Platform (Middleware).
					\end{itemize}
                    \item[] April 2021 - Dec. 2021 \tabto{5cm} PM \& Senior Software Engineer (Py, PHP, n8n, R-Pi, Bubble) \hfill Kitaky\=ush\=u -- Japan
					\begin{itemize}
                        \item[+] Project Manager for SaaS platform for coworking spaces for \textbf{HOA}. Product design, DB tuning \& Backend workflows. Process analysis, productivity assessment, training, consulting and B2B Tools (Slack, Jira, Confluence).
                        \item[+] Facial recognition project in IoT (Raspberry Pi, Python, ThingsBoard, MQTT).
					\end{itemize}
					\item[] Feb.  2018 - May 2019 \tabto{5cm} DevOps (Python, Jenkins, Groovy, GCP, PowerShell, Docker) \hfill Ghent -- Belgium
					\begin{itemize}
                        \item[] Promotion of software quality across \textbf{Around Media}.
                        \begin{itemize}
                            \item[+] Jenkins \& Google CP to pipeline 1200+ UE4 builds, releases, migration of assets, VM backups \& cloning.
                            \item[+] Creation of \ifisanon \texttt{github.com/...} \textit{(Anonymous)}, \else \texttt{https://github.com/Mulugruntz/jam} \fi to save 500\euro+ / GCE instance monthly.
                        \end{itemize}
					\end{itemize}
					\item[] April 2017 - Jan. 2018 \tabto{5cm} Software Engineer (Python, Django, MariaDB, Postgres, Docker) \hfill Hasselt -- Belgium
					\begin{itemize}
						\item[] MVP Developer for  \textbf{Unleashed} (mobile telco) in a Kanban + Squad environment.
						\begin{itemize}
							\item[+] Studies, performance tuning, implementation of new features, bugfix and code reviews.
						\end{itemize}
					\end{itemize}
					\item[] \textbf{Since July 2016} \tabto{5cm} Independent Python Contractor \hfill Nice Area -- France
					\begin{itemize}
						\item[+] Private financial market project. Python \& Django missions. Python trainer for \textbf{AlterWay}, St Cloud, France.
					\end{itemize}
					\item[] Feb. 2016 - June 2016 \tabto{5cm} IT Executive (Java, Python, R-Pi, Linux) \hfill Nice Area -- France
					\begin{itemize}
						\item[] Lightning Project for \textbf{PwC} (IoT \& B2B, Raspberry Pi), through SII. Creation of :
						\begin{itemize}
							\item[+] Generic persistence layer, called in REST and its Json implementation. Java / ServiceMix / Karaf.
							\item[+] System Watchdog taking XMPP commands with a module-defined grammar. Python / Shell/ smx / init.d.
							\item[+] Python (eg. DTMF \& Morse Code wrapping SoX) and Front (HTML, Bootstrap \& uikit, Angular 1.5).
						\end{itemize}
					\end{itemize}
								\item[] Nov. 2015 - Feb. 2016 \tabto{5cm} IT Engineer (PHP, Java, C++, Linux) \hfill Nice Area -- France
												\begin{itemize}
																\item[] Classified project for \textbf{Airbus D\&S}, through Antyas. It involved, among others, SPOT satellites' image processing.
												\end{itemize}
                \item[] Oct. 2012 - July 2015 \tabto{5cm} IT Engineer (C++, Python, Sqlite, Oracle) \hfill Nice Area -- France
                \begin{itemize}
                        \item[] In Data Replication team within \textbf{Amadeus}' Middleware department. Mainly focused on R\&D, I worked on:
                        \begin{itemize}
                                \item[+] designing new solutions to improve overall performance (network, database, algorithms).
                                \item[+] data replication over thousands of nodes. The type of data is either static or extremely dynamic.
                                \item[+] designing and implementing abstract types for consistency and bridge Oracle $\rightleftarrows$ C++ $\rightleftarrows$ Sqlite $\rightleftarrows$ Python.
                                \item[+] various scripts to prototype or automatize tasks: storage / retrieval / backup / cleanup after each build\textellipsis
                                \item[+] exporting data from our caches into two iterations of XMLs, generating XSLTs and XSDs from meta-XSLTs. This design allowed us to publish XML data into past and present schema versions.
																\item[+] designed and implemented modified Hepburn algorithm for Japanese transliteration.
																\item[+] decommissioned legacy terminal entries from IBM TPF system into Amadeus' new C++ architecture: OBE.
                        \end{itemize}
                \end{itemize}
                \item[] May 2012 - Aug. 2012 \tabto{5cm} MSc Dissertation (Python/Django, JS, HTML5/CSS3, \LaTeX{}) \hfill Edinburgh -- Scotland
%                \begin{itemize}
%                        \item[] Creation of a board game Framework (multiplayer, concurrent, real-time, async, server-side event-driven).
%                \end{itemize}
                \item[] Summer 2011 \tabto{5cm} Freelance (PHP, JS, HTML5/CSS3) \hfill Montauban -- France
                \begin{itemize}
                        \item[] Creation of the website \ifisanon \texttt{www....com} \textit{(Anonymous)}, \else \texttt{www.qualigraphe.com}, \fi and of its custom modular CMS. Visuals provided by the client.
                \end{itemize}
                \item[] Oct. 2010 - May 2011 \tabto{5cm} Honours Project (PHP, JS, HTML/CSS) \hfill Aberdeen -- Scotland
%                \begin{itemize}
%                        \item[] Created a piece of software that provides protection and license management to web developers.
%                \end{itemize}
                \item[] Feb. - May 2009 \tabto{5cm} Observation placement in Middle School (Technology) \hfill Montauban -- France
                \item[] June - Aug. 2008 \tabto{5cm} Internship (PHP, JS, HTML/CSS) \hfill Toulouse -- France
                \item[] Oct. - Nov. 2007 \tabto{5cm} IT Maintenance for \textbf{CROUS de Toulouse} (public establishment) \hfill Toulouse -- France
        \end{itemize}
        
\section{\faMagic~MISCELLANEOUS}
        \begin{itemize}
                \item[] French driving license
                \item[] \textbf{TOEFL} iBT (June 25, 2011): \textbf{107/120} (Reading 23/30, Listening 27/30, Speaking 29/30, Writing 28/30)
                    \end{itemize} 
 
\section{\faGamepad~HOBBIES}
        \begin{itemize}
                \item[] Dev, weightlifting (5 years), Go, MahJong MCR, boardgames, traveling, baking, hitchhiking, cultural exchanges
        \end{itemize}

\section{\faUserCheck~REFEREES}
\ifisanon 
     \begin{itemize}
         \item[] Referees are available upon request. When the anonymity is removed, do not forget to ask for them. \textit{(Anonymous)}
     \end{itemize}
\else
                \begin{itemize}
                        \item[] Professor Fan Wenfei \tabto{5cm} \texttt{wenfei -at- inf.ed.ac.uk} \hfill \texttt{http://homepages.inf.ed.ac.uk/wenfei}
                        \item[] Dr. Niccolo Capanni \tabto{5cm} \texttt{niccolo -at- capanni.co.uk} \hfill \texttt{http://www.linkedin.com/in/capanni}
                \end{itemize}
\fi
\end{resume} 

\end{document}